\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-20 paper/main.tex
.

\subsection{Evaluation and metrics}

To assess each model, we compute a variety of common metrics for
binary classification. As the datasets are highly imbalanced, we use
the area under the receiver operating characteristic curve
(AUROC) on training, validation and testing split. % We
% calculated the true positive rate (TPR), false positive rate (FPR), and
% precision score. We will further compute true positives (TP), false
% positives (FP), false negatives (FN) and finally true negatives (TN).

@@

We construct a PPI graph with proteins as nodes and protein-protein
interactions as edges, mapping the protein features to each target as
node features. \name then propagates information among the PPI network
utilizing graph convolutional steps, calculating the similarity of
drug and protein representation, and thus eventually predicting
whether there is an interaction. The full workflow scheme is depicted
in figure~\ref{fig:ModelWorkflow}

@@

We trained, validated and finally tested all considered models on the
STITCH dataset using a 5-fold cross-validation over a protein
split; we then selected the best-performing models (with respect to
\textit{AUROC/MacroAUC} and $MicroAUC_p$) and evaluate them on in 5-fold protein split cross validation on the Yamanishi benchmark dataset to avoid validation overfitting and yield more realistic testing results. To evaluate the influence of the different
features separately, and determine whether they ``localize'' on the
PPI graph (and therefore can be exploited successfully by the graph
neural networks), we train and evaluate models with different types of
features, and with and without inclusion of the PPI graph,
separately, comparing the molecular (MolPred) and phenotype based (OntoPred) predictor and a combination of both, concatenating both features.
Table \ref{tab:Results} (a)+(b) shows the results of these experiments.

>>>>

\subsection{Evaluation and metrics}
\label{sec:evaluation}
To assess each model, we compute a variety of common metrics for
binary classification. As the datasets are highly imbalanced, we use
the area under the receiver operating characteristic curve
(AUROC) on training, validation and testing split. % We
% calculated the true positive rate (TPR), false positive rate (FPR), and
% precision score. We will further compute true positives (TP), false
% positives (FP), false negatives (FN) and finally true negatives (TN).

@@

We construct a graph with proteins as nodes and protein-protein
interactions as edges, mapping the protein features to each target as
node features. \name then propagates information among the PPI network
utilizing graph convolutional steps, calculates the similarity of drug
and protein representations, and predicts whether there is an
interaction. The full workflow scheme is depicted in
figure~\ref{fig:ModelWorkflow}

@@

We trained, validated and finally tested all considered models on the
STITCH dataset using a 5-fold cross-validation over a protein split;
we then selected the best-performing models (with respect to
\textit{MacroAUC} and $MicroAUC_p$, see Section \ref{sec:evaluation})
and evaluate them in a 5-fold protein-split cross-validation on the
Yamanishi benchmark dataset to avoid validation overfitting and yield
more realistic testing results. To evaluate the influence of the
different features separately, and to determine whether they
``localize'' on the PPI graph (and therefore can be exploited
successfully by the graph neural networks), we train and evaluate
models with different types of features, and with and without
inclusion of the PPI graph, separately. We comparing the molecular
(MolPred) and phenotype-based (OntoPred) prediction model, and a
combination of both when concatenating both types of features.  Table
\ref{tab:Results} (a)+(b) shows the results of these experiments.
